Robust background subtraction in traffic environments

### 2019-02-16 paper/Paper.tex
paper conclusions

\subsection*{Conclusion}

>>>>

\subsection*{Conclusion}
We have provided a background subtraction system based on the PBAS algorithm. The system is meant to work real time in traffic surveillance scenarios, also under challening environmental conditions and heavy traffic, 24/7. In order to do this, the general purpose PBAS algorithm was studied and the hyperparameters were adapted in order to perform best in this particular scenario. We have validated our work by visual inspection in particular and challenging situations, with long videos with environmental and traffic conditions changing over time. We further experimented with shadow removal methods and we tried to exploit motion informations. Future work can be done in this direction, until arriving to a precise classification of noise and errors in the mask detected. Still, the system as it is now can be employed as a preprocessing step for many anomaly detection applications, such as car accidents, cars going in the wrong direction and people crossing the road.
